An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
out-neighbor -> forward-neighbor

Given a root node $(s, t)$, during the execution the BFS discussed above builds a search tree, denoted by $T(s,t)$,
where nodes are temporally connected.
\begin{lemma}
For a node active at different time stamps, say $(s, t_1)$ and $(s,t_2)$ such that $t_1 \leq t_2$,  we have $T(s, t_2) \subseteq T(s, t_1)$, where $T(s,t_1) = T(s,t_2)$ if and only if 
$t_1 = t_2$.
\end{lemma}
\proof
Trivially, $t_1 =t_2$ if and only if $(s,t_1) = (s,t_2)$ if and only if 
$T(s,t_1) = T(s,t_2)$. Now suppose $t_1 < t_2$.
Let $(v, t)$ be an arbitrary active node that belongs to $T(s, t_2)$. Then there exists an temporal path
(constructed by the evolving graph BFS) from $(s,t_2)$ to $(v,t)$. Since both
$(s,t_1)$ and $(s,t_2)$ are active, $(s,t_2)$ is an out-neighbor of $(s,t_1)$ by definition, i.e., there exists an edge from $(s,t_1)$ to $(s,t_2)$.  Hence there exists a temporal path
from $(s,t_1)$ to $(v,t)$ and so $(v,t) \in T(s,t_1)$.
\endproof

>>>>

Given a root node $(s, t)$, during the execution the BFS discussed above builds a search tree, denoted by $T(s,t)$,
where nodes are temporally connected.
\begin{lemma}
For a node active at different time stamps, say $(s, t_1)$ and $(s,t_2)$ such that $t_1 \leq t_2$,  we have $T(s, t_2) \subseteq T(s, t_1)$, where $T(s,t_1) = T(s,t_2)$ if and only if 
$t_1 = t_2$.
\end{lemma}
\proof
Trivially, $t_1 =t_2$ if and only if $(s,t_1) = (s,t_2)$ if and only if 
$T(s,t_1) = T(s,t_2)$. Now suppose $t_1 < t_2$.
Let $(v, t)$ be an arbitrary active node that belongs to $T(s, t_2)$. Then there exists a temporal path
(constructed by the evolving graph BFS) from $(s,t_2)$ to $(v,t)$. Since both
$(s,t_1)$ and $(s,t_2)$ are active, $(s,t_2)$ is a forward-neighbor of $(s,t_1)$ by definition, i.e., there exists an edge from $(s,t_1)$ to $(s,t_2)$.  Hence there exists a temporal path
from $(s,t_1)$ to $(v,t)$ and so $(v,t) \in T(s,t_1)$.
\endproof
